Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-11-08 2017-EUROPAR/Gamification/paper.tex
Anonymizes  system name
Refs #5 which was already closed, but..

Distributed computing systems can be created using volunteers who
provide their own computing resources or storage to contribute to a common effort. They can, for instance,  run a script embedded in a web page, collaboration is straightforward, but also ephemeral, with resources depending on the amount of time a user lends; this  implies that
the user has to be kept engaged so as to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
NodIO with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment where a gamification technique is applied by adding a leader-board
showing the top scores achieved by registered contributors. In the NodIO system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation.
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\% of the work.

@@

In this experiment a gamification technique is applied to
the {\sf NodIO} volunteer computing framework, using the
particular version described in \cite{DBLP:conf/gecco/MereloCGCRV16,2016arXiv160101607M}.
The objective of the experiment is to test the kind of impact
applying a gamification technique has on user engagement in this
particular application. In order to apply a rewarding system
user authentication had to be developed first. In earlier designs
this functionality was not desired because it was seen as a barrier
for participation. After all, the advantage of a browser based volunteer system
is precisely the minimum amount of user intervention needed to start.
The last thing a user wants to see is yet another registration form.
Then, the first design decision for this version is that registration is optional and simple as shown in Figure \ref{fig:login}.

@@

After login, registered users are welcomed by their name, and they can see
their score and level. All users can see in a modal dialog the leader board.
While the modal is opened, the scores are refreshed every second. All other
functionality is available to all users and is the same as the previous
{\sf NodIO} version, showing the state of the current algorithm.
In the front page a link to the open source code of the experiment was also
available \url{https://undisclos.ed}
% \url{https://github.com/lucero21/login-master}

@@

The objective of this work was to test the kind of impact
applying a gamification technique has on user engagement in
the {\sf NodIO} volunteer computing framework; In concordance with
the results obtained in other
browser-based volunteer systems, after
applying the gamification techniques, user participation was increased.

>>>>

Distributed computing systems can be created using volunteers who decide to
provide their own  resources or storage to contribute to a common effort. They can, for instance, run a script embedded in a web page, collaboration is straightforward, but also ephemeral, with resources depending on the amount of time a user lends; this  implies that 
the user has to be kept engaged so as to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
% NodIO
Anonymous with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment where a gamification technique is applied by adding a leader-board
showing the top scores achieved by registered contributors. In the
% NodIO
Anonymous system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation.
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\% of the work.

@@

In this experiment a gamification technique is applied to
the Anonymous
% {\sf NodIO}
volunteer computing framework, using the
particular version described in \cite{DBLP:conf/gecco/MereloCGCRV16,2016arXiv160101607M}.
The objective of the experiment is to test the kind of impact
applying a gamification technique has on user engagement in this
particular application. In order to apply a rewarding system
user authentication had to be developed first. In earlier designs
this functionality was not desired because it was seen as a barrier
for participation. After all, the advantage of a browser based volunteer system
is precisely the minimum amount of user intervention needed to start.
The last thing a user wants to see is yet another registration form.
Then, the first design decision for this version is that registration is optional and simple as shown in Figure \ref{fig:login}.

@@

After login, registered users are welcomed by their name, and they can see
their score and level. All users can see in a modal dialog the leader board.
While the modal is opened, the scores are refreshed every second. All other
functionality is available to all users and is the same as the previous
%{\sf NodIO}
Anonymous version, showing the state of the current algorithm.
In the front page a link to the open source code of the experiment was also
available \url{https://undisclos.ed}
% \url{https://github.com/lucero21/login-master}

@@

The objective of this work was to test the kind of impact
applying a gamification technique has on user engagement in
the Anonymous
% {\sf NodIO}
volunteer computing framework; In concordance with
the results obtained in other
browser-based volunteer systems, after
applying the gamification techniques, user participation was increased.
